Floral resource choice by bumble bee species in the Berchtesgadener Alps

### 2020-11-30 analyses/niche_relations_v6.Rmd
went ordi surfing

---
title: "Dietary niche relationships between core bumble bee species in the Berchtesgadener Alps"
output: html_document
---

# Prepare workspace
## Load packages 
```{r message=FALSE, warning=FALSE, include=FALSE, echo = FALSE}
library(bipartite)
library(mgcv)
library(mgcViz)
library(vegan)
library(ggvegan)
library(ggrepel)
library(treemapify)
library(RColorBrewer)
library(tidyverse)
library(lubridate)
library(patchwork)
library(tidymodels)
```

@@

# BB traits
bb_traits <- read_csv("../processed_data/bb_traits.csv") %>%
  mutate(pbl.fac = factor(if_else(
    bb.sp %in% c("hort", "pasc", "wurf", "gers", "mend", "hypn"), "long", "short"))
    )

@@

## Flower colors
fl_color <- read_csv("../processed_data/floral_color.csv")

@@

## join all trait tables
fl_traits <- fl_tax %>%
  full_join(fl_ktype) %>%
  full_join(fl_color) %>%
  full_join(fl_morph) %>%
  dplyr::select(plant.sp, plant.genus, plant.family, k.type, k.type.s, k.type.ss, color, diam, LN)

# Network
net <- read_csv("../processed_data/network.csv") %>%
  mutate(year = factor(year)) %>% # convert year to factor
  left_join(site_data, by = "site") %>% # add site data
  ungroup() %>%
  arrange(site, date) %>%
  left_join(fl_traits) %>% # add floral traits
  #group_by(elev.class2) %>%
  group_by(site) %>%
  mutate(period = cut_interval(dayofyear, 4, labels = c("early", "mid1", "mid2", "late"))) # divide each elev.class2 into 3 equal time slices

# Floral survey
survey <- read_csv("../processed_data/floral_survey.csv") %>%
  filter(flower.cover > 0) %>% # only count plants in bloom
  semi_join(net, by = "plant.sp") %>% # Consider only plants visited (anytime anywhere, not specifically for a given site*date)
  dplyr::select(site, date, plant.sp, flower.cover) %>%
  left_join(fl_traits) # add floral traits

missing_colors <- net %>%
  bind_rows(survey) %>%
  ungroup() %>%
  select(plant.sp, color) %>%
  filter(is.na(color)) %>%
  distinct()
```

We will focus on six species that are abundant and widespread:  
  1. *B. sensu-strictu*
  2. *B. pascuorum*
  3. *B. pratorum*
  4. *B. hortorum*
  5. *B. soroensis*
  6. *B. wurflenii*

@@

And we will parse the samples by elevation class and season, dividing the samples from each site into equal-interval thirds
```{r}
samples <- net %>%
  filter(bb.sp %in% c("bss", "pasc", "prat", "hort", "soro", "wurf")) %>% # focal species
  #group_by(elev.class2) %>%
  group_by(site) %>%
  mutate(period = cut_interval(dayofyear, 4, labels = c("early", "mid1", "mid2", "late"))) %>%
  group_by(site, period, dayofyear) %>%
  summarize(obs = n()) %>%
  left_join(site_data) %>%
  mutate(date = as_date(dayofyear))

ggplot(samples, aes(as_date(yday(date)), elev.mean, color = period)) +
  #geom_point(size = 1, aes(alpha = obs)) +
  geom_point(size = 2, alpha = 0.75) +
  #facet_wrap(~year) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_alpha_continuous(name = "Observations") +
  scale_x_date(date_labels = "%b", breaks = as_date(c("1970-04-01", "1970-05-01", "1970-06-01",
                                                    "1970-07-01", "1970-08-01", "1970-09-01"))) +
  #geom_hline(yintercept = c(755, 1500), linetype = "dashed") +
  theme_light(12) +
  labs(x = "Time",
       y = "Elevation (m x 10)") 
```

## Define functions
```{r, echo = FALSE}
# Convert PCoA to tidy array ("fortify")
# pcoa_fort <- function(x){
#   fortify(x, axes = 1:2) %>% 
#   mutate(Score = case_when( # rename default scores to match my data
#     Score == "species" ~ "FL sp.",
#     Score == "sites" ~ "BB sp."))
# }

pcoa_fort <- function(x){
  fortify(x, axes = 1:2) %>% 
  mutate(Score = case_when( # rename default scores to match my data
    Score == "species" ~ "flora",
    #Label %in% c("hort", "pasc", "wurf") ~ "LT spp.",
    Label %in% c("hort", "pasc") ~ "LT spp.",
    Label == "wurf" ~ "robber",
    Label %in% c("bss", "soro", "prat") ~ "ST spp."))
}

# Plot PCoA; to avoid overplotting, scores < min_score are not plotted
pcoa_plot <- function(x, min_score = 0.25) {

  # # Add T.class variable for the BB.sp subset of the PCoA
  # t.class <- x %>%
  #   filter(Score == "BB sp.") %>%
  #   mutate(T.class = factor(if_else(
  #     Label %in% c("hort", "pasc", "wurf", "gers", "mend", "hypn"), "long", "short"))
  #     )

  cols <- c("flora" = "gray40", "LT spp." = "#F8766D", "ST spp." = "#00BA38", "robber" = "#619CFF")

  ggplot(filter(x, (abs(MDS1) > min_score | abs(MDS2) > min_score) | (Score %in% c("LT spp.", "ST spp.", "robber"))), 
         aes(MDS1, MDS2, color = Score)) + # no threshold for BB spp
    #geom_polygon(data = t.class, aes(MDS1, MDS2, linetype = T.class), # draw polygons around T classes
     #            color = "gray70", fill = NA, size = 1.25, key_glyph = "abline") +
    geom_point(size = 2, alpha = 0.75) + # add points
    ggrepel::geom_text_repel(aes(label = Label), key_glyph = "rect", size = 3) + # add labels
    coord_fixed() + # Gavin Simpson says this is **really** important
    theme_classic() +
    theme(legend.title=element_blank()) +
    scale_color_manual(values = cols)
}

@@

  x %>%
    filter(caste != "male") %>%
    filter(bb.sp %in% c("bss", "pasc", "prat", "hort", "soro", "wurf")) %>% # only focal species
    group_by(..., bb.sp, !!criterion) %>% # pooling all sites and years
    summarize(freq = n()) %>% # get interaction frequency for each BB-FL pair
    group_by(..., bb.sp) %>%
    mutate(prop = freq/sum(freq)) %>% # get proportional interaction frequency for each BB-FL pair
    dplyr::select(-freq) %>% # drop freq variable
    group_by(...) %>%
    nest() %>% # nest into list-column
    mutate(comm1 = map(data, # spread into the kind of array vegan likes
                       function(x) pivot_wider(x, names_from = !!criterion, values_from = prop) %>%
                         replace(is.na(.), 0)
                       ), 
           comm2 = map(comm1, # column to rowname
                       function(x) column_to_rownames(x, var = "bb.sp")
                       ),
           pcoa = map(comm2, # call PCoA
                      function(x) capscale(x ~ 1, distance = "horn")
                      ),
           traits = map(comm1, # join BB traits
                        function(x) x %>% 
                          left_join(y) %>% # y is the trait table, an argument in the main function call
                          column_to_rownames(var = "bb.sp") %>% 
                          select(pbl.fac) # pbl.fac is the variable I'm interested in
                        ),
           # adonis = map2(comm2, traits, # run adonis permuatation test for distance ~ tongue class
           #               function(x, y) adonis(x ~ pbl.fac, data = y, method = "horn")
           #               ),
           # betadis = map2(comm2, traits, # betadisper to test for difference in dispersion between tongue classes
           #               function(x, y) x %>%
           #                 vegdist(method = "horn") %>% # betadisper runs a PCoA under the hood; match method to my PCoA
           #                 betadisper(group = y$pbl.fac) 
           #               ),
           # betadis.permutest = map(betadis, permutest), # perumutation test
           # betadis.p = map(betadis.permutest, # extract betadisper p-value
           #                 function(x) x$tab$'Pr(>F)'[[1]]
           #                 ),
           # betadis.boxplot = map(betadis, boxplot), # boxplot of betadisper
           pcoa.fort = map(pcoa, pcoa_fort), 
           pcoa.plot = map(pcoa.fort, pcoa_plot),
           # adonis.r2 = map(adonis, # extract adonis r2
           #                 function(x) x$aov.tab$R2[[1]]
           #                 ),
           # adonis.p = map(adonis, # extract adonis p-value
           #                function(x) x$aov.tab$'Pr(>F)'[[1]]
           #                ),
           MDS1 = map(pcoa, # extract variance explained by MDS1
                      function(x) x$CA$eig[[1]] / sum(x$CA$eig)
                      ), 
           MDS2 = map(pcoa, # extract variance explained by MDS2
                      function(x) x$CA$eig[[2]] / sum(x$CA$eig)
                      )) %>%
    #unnest(cols = c(adonis.r2, adonis.p, betadis.p, MDS1, MDS2)) %>% # these are lists of length = 1, so unnesting them simply displays the value
    unnest(cols = c(MDS1, MDS2)) %>% # these are lists of length = 1, so unnesting them simply displays the value
    # select(..., comm2, pcoa, betadis, betadis.permutest, betadis.p, adonis, 
    #        adonis.r2, adonis.p, betadis.boxplot, pcoa.plot, MDS1, MDS2) 
    select(..., comm2, pcoa, pcoa.plot, MDS1, MDS2)
}

beta_func <- function(x, traits, sitedata, level, criterion, binary, ...) {

@@

# For the floral survey data
beta_func_fl <- function(x, sitedata, criterion, binary, ...) {

@@

## Taxonomic and morphological together
pdf("../analyses/output/niche_pcoa.pdf", height = 8.5, width = 11)
(niche.tax.plot + ggtitle("Taxonomic") | niche.morph.plot + ggtitle("Morphological")) + plot_layout(guides = 'collect') 
dev.off()
```

@@

## 1.6 Tree plots
This visualization deserves to be pulled out as a stand-alone chunk. It's so good.
```{r}
### Visitation by BB species, parsed by elev.class2 and period
visitation_abund.sp <- net %>%
  filter(caste != "male") %>%
  #filter(bb.sp %in% c("bss", "pasc", "prat", "hort", "soro", "wurf")) %>% # only focal species
  #group_by(elev.class2) %>%
  group_by(site) %>%
  mutate(period = cut_interval(dayofyear, 4, labels = c("early", "mid1", "mid2", "late"))) %>%
  # mutate(k.type.ss = factor(k.type.ss),
  #        color = factor(color),
  #        bb.sp = factor(bb.sp, levels = c("hort", "pasc", "wurf", "bss", "prat", "soro"))) %>%
  mutate(k.type.ss = factor(k.type.ss),
         color = factor(color),
         bb.sp = factor(bb.sp)) %>%
  group_by(period, elev.class2, plant.sp.abb, plant.genus, k.type.ss, color, plant.family, bb.sp) %>%
  summarize(abund = n()) %>%
  group_by(elev.class2, period, bb.sp) %>%
  mutate(prop = abund/sum(abund)) %>%
  arrange(elev.class2, period, bb.sp, -prop)

@@

# Early
tp.early <- ggplot(filter(visitation_abund.sp, period == "early"), 
                aes(area = prop, fill = k.type.ss, label = plant.sp.abb)) +
  geom_treemap(color = "white") +
  geom_treemap_text(fontface = "italic", color = "black", place = "centre", "grow" = TRUE, alpha = 0.5) +
  scale_fill_manual(values = cols) + 
  labs(fill = "Morphotype") +
  facet_grid(fct_rev(elev.class2)~bb.sp) +
  theme(strip.text = element_text(size = 14))

tp.early.col <- ggplot(filter(visitation_abund.sp, period == "early"), 
                aes(area = prop, fill = color, label = plant.sp.abb)) +
  geom_treemap(color = "white") +
  geom_treemap_text(fontface = "italic", color = "black", place = "centre", "grow" = TRUE, alpha = 0.5) +
  scale_fill_manual(values = cols2) + 
  labs(fill = "Morphotype") +
  facet_grid(fct_rev(elev.class2)~bb.sp) +
  theme(strip.text = element_text(size = 14))

# Mid
tp.mid1 <- ggplot(filter(visitation_abund.sp, period == "mid1"), 
                 aes(area = prop, fill = k.type.ss, label = plant.sp.abb)) +
  geom_treemap(color = "white") +
  geom_treemap_text(fontface = "italic", color = "black", place = "centre", "grow" = TRUE, alpha = 0.5) +
  scale_fill_manual(values = cols) + 
  labs(fill = "Morphotype") +
  facet_grid(fct_rev(elev.class2)~bb.sp) +
  theme(strip.text = element_text(size = 14))

tp.mid1.col <- ggplot(filter(visitation_abund.sp, period == "mid1"), 
                 aes(area = prop, fill = color, label = plant.sp.abb)) +
  geom_treemap(color = "white") +
  geom_treemap_text(fontface = "italic", color = "black", place = "centre", "grow" = TRUE, alpha = 0.5) +
  scale_fill_manual(values = cols2) + 
  labs(fill = "Morphotype") +
  facet_grid(fct_rev(elev.class2)~bb.sp) +
  theme(strip.text = element_text(size = 14))

tp.mid2 <- ggplot(filter(visitation_abund.sp, period == "mid2"), 
                 aes(area = prop, fill = k.type.ss, label = plant.sp.abb)) +
  geom_treemap(color = "white") +
  geom_treemap_text(fontface = "italic", color = "black", place = "centre", "grow" = TRUE, alpha = 0.5) +
  scale_fill_manual(values = cols) + 
  labs(fill = "Morphotype") +
  facet_grid(fct_rev(elev.class2)~bb.sp) +
  theme(strip.text = element_text(size = 14))

tp.mid2.col <- ggplot(filter(visitation_abund.sp, period == "mid2"), 
                 aes(area = prop, fill = color, label = plant.sp.abb)) +
  geom_treemap(color = "white") +
  geom_treemap_text(fontface = "italic", color = "black", place = "centre", "grow" = TRUE, alpha = 0.5) +
  scale_fill_manual(values = cols2) + 
  labs(fill = "Morphotype") +
  facet_grid(fct_rev(elev.class2)~bb.sp) +
  theme(strip.text = element_text(size = 14))

# Late
tp.late <- ggplot(filter(visitation_abund.sp, period == "late"), 
                  aes(area = prop, fill = k.type.ss, label = plant.sp.abb)) +
  geom_treemap(color = "white") +
  geom_treemap_text(fontface = "italic", color = "black", place = "centre", "grow" = TRUE, alpha = 0.5) +
  scale_fill_manual(values = cols) + 
  labs(fill = "Morphotype") +
  facet_grid(fct_rev(elev.class2)~bb.sp) +
  theme(strip.text = element_text(size = 14))

tp.late.col <- ggplot(filter(visitation_abund.sp, period == "late"), 
                  aes(area = prop, fill = color, label = plant.sp.abb)) +
  geom_treemap(color = "white") +
  geom_treemap_text(fontface = "italic", color = "black", place = "centre", "grow" = TRUE, alpha = 0.5) +
  scale_fill_manual(values = cols2) + 
  labs(fill = "Morphotype") +
  facet_grid(fct_rev(elev.class2)~bb.sp) +
  theme(strip.text = element_text(size = 14))

# Pair with ordination plots
tp_ord1 <- (
  tp.early | (
    niche_high_early.tax.plot / 
    niche_mid_early.tax.plot / 
    niche_low_early.tax.plot
    ) + 
    plot_layout(guides = 'collect')
  ) + 
  plot_layout(widths = c(5, 1))
ggsave("./output/tree_ord_early.png", tp_ord1, width = 14, height = 8)

>>>>

---
title: "Floral resource choice by bumble bee species in the Berchtesgadener Alps"
output: html_document
---

# Prepare workspace
## Load packages 
```{r message=FALSE, warning=FALSE, include=FALSE, echo = FALSE}
library(bipartite)
library(mgcv)
library(mgcViz)
library(vegan)
library(ggvegan)
library(ggrepel)
library(treemapify)
#library(RColorBrewer)
library(tidyverse)
library(lubridate)
library(patchwork)
library(tidymodels)
```

@@

# BB traits
bb_traits <- read_csv("../processed_data/bb_traits.csv")

@@

## Flower colors (accessed through BioFlor)
fl_color <- read_csv("../processed_data/floral_color.csv")

@@

## join all floral trait tables
fl_traits <- fl_tax %>%
  full_join(fl_ktype) %>%
  full_join(fl_color) %>%
  full_join(fl_morph) %>%
  dplyr::select(plant.sp, plant.genus, plant.family, k.type, k.type.s, k.type.ss, color, diam, LN)

# Network
net <- read_csv("../processed_data/network.csv") %>%
  mutate(year = factor(year)) %>% # convert year to factor
  left_join(site_data, by = "site") %>% # add site data
  ungroup() %>%
  arrange(site, date) %>%
  left_join(fl_traits) %>% # add floral traits
  group_by(site) %>%
  mutate(period = cut_interval(dayofyear, 4, labels = c("early", "mid1", "mid2", "late"))) # divide each elev.class2 into 4 equal time slices

# Floral survey
survey <- read_csv("../processed_data/floral_survey.csv") %>%
  filter(flower.cover > 0) %>% # only count plants in bloom
  semi_join(net, by = "plant.sp") %>% # Consider only plants visited (anytime anywhere, not specifically for a given site*date)
  dplyr::select(site, date, plant.sp, flower.cover) %>%
  left_join(fl_traits) # add floral traits
```

Core species:  
  1. *B. sensu-strictu*
  2. *B. pascuorum*
  3. *B. pratorum*
  4. *B. hortorum*
  5. *B. soroensis*
  6. *B. wurflenii*

@@

We will parse the samples by elevation class and season, dividing the samples from each site into equal-interval quarters
```{r}
samples <- net %>%
  filter(bb.sp %in% c("bss", "pasc", "prat", "hort", "soro", "wurf")) %>% # focal species
  #group_by(elev.class2) %>%
  group_by(site) %>%
  mutate(period = cut_interval(dayofyear, 4, labels = c("early", "mid1", "mid2", "late"))) %>%
  group_by(site, period, dayofyear) %>%
  summarize(obs = n()) %>%
  left_join(site_data) %>%
  mutate(date = as_date(dayofyear))

ggplot(samples, aes(as_date(yday(date)), elev.mean, color = period)) +
  #geom_point(size = 1, aes(alpha = obs)) +
  geom_point(size = 2, alpha = 0.75) +
  #facet_wrap(~year) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_alpha_continuous(name = "Observations") +
  scale_x_date(date_labels = "%b", breaks = as_date(c("1970-04-01", "1970-05-01", "1970-06-01",
                                                    "1970-07-01", "1970-08-01", "1970-09-01"))) +
  geom_hline(yintercept = c(900, 1500), linetype = "dashed") +
  theme_light(12) +
  labs(x = "Time",
       y = "Elevation (m x 10)") 
```

## Define functions
```{r, echo = FALSE}
# Fortify envfit() object fitted to BB tongue length data
envfit_fort <- function(x){
  fortify(x) %>%
  select(Score = Type, Label, MDS1, MDS2) %>%
  mutate(Label = case_when(Label == "pbl.w" ~ "T.len"),
         Score = case_when(Score == "Vector" ~ "T.len"))
}

# Fortify PCOA and add the results of an envfit() to BB tongue length
pcoa_fort <- function(x, y){
  fortify(x, axes = 1:2) %>%
  bind_rows(y) %>%
  mutate(Score = case_when(
    Score == "species" ~ "FL.sp",
    Score == "sites" ~ "BB.sp",
    Score == "T.len" ~ "T.len"))
}

# Plot PCoA ordination with arrow for tongue length envfit()
pcoa_plot <- function(x, y, min_load = 0.25) {
  ggplot(filter(x, (abs(MDS1) > min_load | abs(MDS2) > min_load) | (Score %in% c("BB.sp", "T.len")))) + # to avoid overplotting, we can filter to include only floral species > loading threshold
    geom_point(aes(MDS1, MDS2, color = Score)) +
    geom_text_repel(aes(MDS1, MDS2, color = Score, label = Label), key_glyph = "rect") +
    geom_segment(data = y, 
               aes(x = 0, y = 0, xend = MDS1, yend = MDS2, colour = Label),
               arrow = arrow(), size = 2, alpha = 0.5, key_glyph = "rect") +
    theme_light() +
    coord_fixed() # Gavin Simpson says this is **really** important
}

@@

  x %>%
    filter(caste != "male") %>%
    filter(!bb.sp %in% c("psit", "gers", "humi")) %>% # omit parasitic species, gers because it's a specialist, humi because it's so rare
    group_by(..., bb.sp, !!criterion) %>% # pooling all sites and years
    summarize(freq = n()) %>% # get interaction frequency for each BB-FL pair
    group_by(..., bb.sp) %>%
    mutate(prop = freq/sum(freq)) %>% # get proportional interaction frequency for each BB-FL pair
    dplyr::select(-freq) %>% # drop freq variable
    group_by(...) %>%
    nest() %>% # nest into list-column
    mutate(comm1 = map(data, # spread into the kind of array vegan likes
                       function(x) pivot_wider(x, names_from = !!criterion, values_from = prop) %>%
                         replace(is.na(.), 0)
                       ), 
           comm2 = map(comm1, # column to rowname
                       function(x) column_to_rownames(x, var = "bb.sp")
                       ),
           pcoa = map(comm2, # call PCoA
                      function(x) capscale(x ~ 1, distance = "horn")
                      ),
           traits = map(comm1, # join BB traits
                        function(x) x %>% 
                          left_join(y) %>% # y is the trait table, an argument in the main function call
                          column_to_rownames(var = "bb.sp") %>% 
                          select(pbl.w) # pbl.w is the variable I'm interested in
                        ),
           adonis = map2(comm2, traits, # run adonis permuatation test for distance ~ tongue class
                         function(x, y) adonis(x ~ pbl.w, data = y, method = "horn")
                         ),
           envfit = map2(pcoa, traits, function(x, y) envfit(x, y)),
           envfit.fort = map(envfit, envfit_fort),
           pcoa.fort = map2(pcoa, envfit.fort, pcoa_fort),
           pcoa.plot = map2(pcoa.fort, envfit.fort, pcoa_plot), 
           envfit.r2 = map(envfit, function(x) x$vectors$r),
           envfit.p = map(envfit, function(x) x$vectors$pvals),
           adonis.r2 = map(adonis, # extract adonis r2
                           function(x) x$aov.tab$R2[[1]]
                           ),
           adonis.p = map(adonis, # extract adonis p-value
                          function(x) x$aov.tab$'Pr(>F)'[[1]]
                          ),
           ordisurf = map2(pcoa, traits, function(x, y) ordisurf(x ~ pbl.w, data = y, k = 8)),
           ordisurf.dev_exp = map(ordisurf, function(x) summary(x)$dev.expl),
           ordisurf.p = map(ordisurf, function(x) summary(x)$s.pv),
           MDS1 = map(pcoa, # extract variance explained by MDS1
                      function(x) x$CA$eig[[1]] / sum(x$CA$eig)
                      ), 
           MDS2 = map(pcoa, # extract variance explained by MDS2
                      function(x) x$CA$eig[[2]] / sum(x$CA$eig)
                      )) %>%
    unnest(cols = c(ordisurf.dev_exp, ordisurf.p, envfit.r2, envfit.p, adonis.r2, adonis.p, MDS1, MDS2)) %>% # these are lists of length = 1, so unnesting them simply displays the value
    select(..., comm2, traits, pcoa, ordisurf, ordisurf.dev_exp, ordisurf.p, envfit, envfit.fort, pcoa.fort, pcoa.plot, envfit.r2, envfit.p, adonis.r2, adonis.p, MDS1, MDS2)
}

ordi1 <- ordisurf(niche.tax$pcoa[[1]] ~ pbl.w, data = niche.tax$traits[[1]])

# Calculate site-wise beta diversity from visitation data
beta_func <- function(x, traits, sitedata, level, criterion, binary, ...) {

@@

# Calculate site-wise beta diversity from survey data
beta_func_fl <- function(x, sitedata, criterion, binary, ...) {

@@

## Taxonomic and morphological together
pdf("../analyses/output/niche_pcoa.pdf", height = 8.5, width = 11)
(niche.tax.plot + ggtitle("Taxonomic") | niche.morph.plot + ggtitle("Morphological")) + plot_layout(guides = 'collect') 
dev.off()

# Playing with ordisurf as alternative to envfit()
library(ggordiplots)

## Based on https://oliviarata.wordpress.com/2014/07/17/ordinations-in-ggplot2-v2-ordisurf/
# Get ordination object
ordi1 <- niche.tax$ordisurf[[1]] 
ordi1.grid <- ordi1$grid #extracts the ordisurf object
ordi1.mite <- expand.grid(x = ordi1.grid$x, y = ordi1.grid$y) #get x and ys
ordi1.mite$z <- as.vector(ordi1.grid$z) #unravel the matrix for the z scores
ordi1.mite.na <- data.frame(na.omit(ordi1.mite)) %>% #gets rid of the nas
  as_tibble() %>%
  rename(MDS1 = x, MDS2 = y)

# Get scores
scores <- fortify(niche.tax$pcoa[[1]], axes = 1:2) %>%
  mutate(Score = case_when(
    Score == "species" ~ "FL.sp",
    Score == "sites" ~ "BB.sp")
    ) %>%
  as_tibble()

# Plot
dat <- filter(scores, (abs(MDS1) > 0.25 | abs(MDS2) > 0.25) | Score == "BB.sp")

ggplot(dat, aes(MDS1, MDS2, pch = Score)) +
  geom_contour(data = ordi1.mite.na, aes(MDS1, MDS2, z = z, color = stat(level)), size = 1.5, alpha = 0.75, inherit.aes = FALSE) +
  geom_point(size = 2) +
  geom_text_repel(aes(MDS1, MDS2, label = Label), key_glyph = "rect") +
  theme_light() +
  scale_color_viridis_c(name = "Tongue length") +
  scale_shape_manual(values = c(16, 1), name = "Level") +
  coord_fixed() # Gavin Simpson says this is **really** important
```

@@

## 1.6 Tree plots
This visualization deserves to be pulled out as a stand-alone chunk. It's so good.
```{r}
### Visitation by BB species, parsed by elev.class2 and period
visitation_abund.sp <- net %>%
  filter(caste != "male") %>%
  filter(!bb.sp %in% c("psit", "gers", "humi")) %>% # only focal species
  #group_by(elev.class2) %>%
  group_by(site) %>%
  mutate(period = cut_interval(dayofyear, 4, labels = c("early", "mid1", "mid2", "late"))) %>%
  # mutate(k.type.ss = factor(k.type.ss),
  #        color = factor(color),
  #        bb.sp = factor(bb.sp, levels = c("hort", "pasc", "wurf", "bss", "prat", "soro"))) %>%
  mutate(k.type.ss = factor(k.type.ss),
         color = factor(color),
         bb.sp = factor(bb.sp)) %>%
  group_by(period, elev.class2, plant.sp.abb, plant.genus, k.type.ss, color, plant.family, bb.sp) %>%
  summarize(abund = n()) %>%
  group_by(elev.class2, period, bb.sp) %>%
  mutate(prop = abund/sum(abund)) %>% 
  left_join(bb_traits) %>%
  arrange(elev.class2, period, bb.sp, -prop)

@@

# Early
tp.early <- ggplot(filter(visitation_abund.sp, period == "early"), 
                aes(area = prop, fill = k.type.ss, label = plant.sp.abb)) +
  geom_treemap(color = "white") +
  geom_treemap_text(fontface = "italic", color = "black", place = "centre", "grow" = TRUE, alpha = 0.5) +
  scale_fill_manual(values = cols) + 
  labs(fill = "Morphotype") +
  facet_grid(fct_rev(elev.class2)~reorder(bb.sp, pbl.w)) +
  theme(strip.text = element_text(size = 14))

tp.early.col <- ggplot(filter(visitation_abund.sp, period == "early"), 
                aes(area = prop, fill = color, label = plant.sp.abb)) +
  geom_treemap(color = "white") +
  geom_treemap_text(fontface = "italic", color = "black", place = "centre", "grow" = TRUE, alpha = 0.5) +
  scale_fill_manual(values = cols2) + 
  labs(fill = "Morphotype") +
  facet_grid(fct_rev(elev.class2)~reorder(bb.sp, pbl.w)) +
  theme(strip.text = element_text(size = 14))

# Mid
tp.mid1 <- ggplot(filter(visitation_abund.sp, period == "mid1"), 
                 aes(area = prop, fill = k.type.ss, label = plant.sp.abb)) +
  geom_treemap(color = "white") +
  geom_treemap_text(fontface = "italic", color = "black", place = "centre", "grow" = TRUE, alpha = 0.5) +
  scale_fill_manual(values = cols) + 
  labs(fill = "Morphotype") +
  facet_grid(fct_rev(elev.class2)~reorder(bb.sp, pbl.w)) +
  theme(strip.text = element_text(size = 14))

tp.mid1.col <- ggplot(filter(visitation_abund.sp, period == "mid1"), 
                 aes(area = prop, fill = color, label = plant.sp.abb)) +
  geom_treemap(color = "white") +
  geom_treemap_text(fontface = "italic", color = "black", place = "centre", "grow" = TRUE, alpha = 0.5) +
  scale_fill_manual(values = cols2) + 
  labs(fill = "Morphotype") +
  facet_grid(fct_rev(elev.class2)~reorder(bb.sp, pbl.w)) +
  theme(strip.text = element_text(size = 14))

tp.mid2 <- ggplot(filter(visitation_abund.sp, period == "mid2"), 
                 aes(area = prop, fill = k.type.ss, label = plant.sp.abb)) +
  geom_treemap(color = "white") +
  geom_treemap_text(fontface = "italic", color = "black", place = "centre", "grow" = TRUE, alpha = 0.5) +
  scale_fill_manual(values = cols) + 
  labs(fill = "Morphotype") +
  facet_grid(fct_rev(elev.class2)~reorder(bb.sp, pbl.w)) +
  theme(strip.text = element_text(size = 14))

tp.mid2.col <- ggplot(filter(visitation_abund.sp, period == "mid2"), 
                 aes(area = prop, fill = color, label = plant.sp.abb)) +
  geom_treemap(color = "white") +
  geom_treemap_text(fontface = "italic", color = "black", place = "centre", "grow" = TRUE, alpha = 0.5) +
  scale_fill_manual(values = cols2) + 
  labs(fill = "Morphotype") +
  facet_grid(fct_rev(elev.class2)~reorder(bb.sp, pbl.w)) +
  theme(strip.text = element_text(size = 14))

# Late
tp.late <- ggplot(filter(visitation_abund.sp, period == "late"), 
                  aes(area = prop, fill = k.type.ss, label = plant.sp.abb)) +
  geom_treemap(color = "white") +
  geom_treemap_text(fontface = "italic", color = "black", place = "centre", "grow" = TRUE, alpha = 0.5) +
  scale_fill_manual(values = cols) + 
  labs(fill = "Morphotype") +
  facet_grid(fct_rev(elev.class2)~reorder(bb.sp, pbl.w)) +
  theme(strip.text = element_text(size = 14))

tp.late.col <- ggplot(filter(visitation_abund.sp, period == "late"), 
                  aes(area = prop, fill = color, label = plant.sp.abb)) +
  geom_treemap(color = "white") +
  geom_treemap_text(fontface = "italic", color = "black", place = "centre", "grow" = TRUE, alpha = 0.5) +
  scale_fill_manual(values = cols2) + 
  labs(fill = "Morphotype") +
  facet_grid(fct_rev(elev.class2)~reorder(bb.sp, pbl.w)) +
  theme(strip.text = element_text(size = 14))

# Pair with ordination plots
tp_ord1 <- (
  tp.early / (
    niche_low_early.tax.plot + ggtitle("low") | 
    niche_mid_early.tax.plot + ggtitle("mid") | 
    niche_high_early.tax.plot + ggtitle("high")
    ) + 
    plot_layout(guides = 'collect')
  ) + 
  plot_layout(heights = c(2, 1))
ggsave("./output/tree_ord_early.png", tp_ord1, width = 16, height = 10)
